DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion

### 2014-07-23 paper/paper.tex
full conditionals alt model
fix paper and fix text cleaner

\[p(a^2 | \nu_0, \tau_0) = IW(\nu_0, \tau_0)\]

\[p(b^2 | \nu_1, \tau_1) = IW(\nu_1, \tau_1)\]

@@

\subsection{Posterior Specification for $b^2$}

\[p(b^2|\beta,\phi) \propto \prod_{t=1}^T \prod_{k=1}^K p(\phi_{kt} | \beta_t, b^2)p(b^2 | \nu_0, \tau_0) \]

\[= \prod_{t=1}^T \prod_{k=1}^K N(\phi_{kt};\beta_t, b^2)IW(\nu_0, \tau_0)\]

\[\propto IW\left(\nu_0 + TK, \left(\tau_0 + \sum_{t=1}^T \sum_{k=1}^K (\phi_{kt} - \beta_t)(\phi_{kt} - \beta_t)^T\right)^{-1}\right)\]

@@

\subsection{Posterior Specification for $a^2$}

\[p(a^2|\alpha,\theta) \propto \prod_{t=1}^T \prod_{i=1}^N \prod_{d=1}^{D_i} p(\theta_{dit} | \alpha_{it}, a^2)p(a^2 | \nu_1, \tau_1) \]

\[= \prod_{t=1}^T \prod_{i=1}^N \prod_{k=1}^K N(\theta_{dit};\alpha_{it}, a^2)IW(\nu_1, \tau_1)\]

This needs to be fixed

\[\propto IW\left(\nu_1 + TND, \left(\tau_0 + \sum_{t=1}^T \sum_{i=1}^N \sum_{d=1}^{D_i} (\theta_{dit} - \alpha_{it})(\theta_{dit} - \alpha_{dit})^T\right)^{-1}\right)\]

@@

>>>>

@@

@@

@@

\section{Full Conditionals for the Alternative Model}

\[p(\gamma_i | \eta, \xi^2) = N(\eta, \xi^2)\]

\[p(\alpha_i|\chi,\sigma^2) = N(\chi, \sigma^2)\]

\[\text{\boldmath$\alpha$} = \{\alpha_1, \alpha_2, ...,\alpha_N\}\]

\[p(\theta_{it}| \alpha_i, \gamma_i,\delta^2) = N(\text{\boldmath$\alpha$}^T \gamma_i, \delta^2)\]

\[p(\phi_k | \beta) = Dir(\beta)\]

\[p(z_{itj}| \theta_{it}) = Mult(\pi(\theta_{it}))\]

\[p(w_{itj} | \phi, z_{itj}) = Mult(\phi_{z_{itj}})\]

\[p(\theta, \phi, \gamma, \alpha, \beta, z | w) \propto \prod_{i=1}^N \prod_{t=1}^T \prod_{j=1}^{J_{ti}} \prod_{k=1}^K p(w_{itj} | \phi, z_{itj}) p(z_{itj} | \theta_{it}) p(\phi_k | \beta) p(\theta_{it} | \alpha_i, \gamma_i, \delta^2) p(\alpha_i | \chi, \sigma^2) p(\gamma_i | \eta, xi^2)\]
